On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2024-07-11 char-4k-bound/char-4k-bound.tex
[4k3] Embrace some fixes from Dr. A.S. Usachev

\title{
	On the characteristic and diameter of planar integral point sets
	\footnote{
		The work of the first author was supported by the Theoretical Physics
		and Mathematics Advancement Foundation “BASIS”.
	}
}

@@

\begin{lemma}
	\label{lem:pre_weeding_I}
	Any set $M = \{A, B, C\} \in \mathfrak{M}_3$ with edge $|AB| = m$, where $|AC| - |BC| = m - s$, $m, s \in \mathbb{N}$, and $s$ is an odd number and $s \leq m$, has a characteristic of the form $p = 4k + 3$, $k \in \mathbb{N}_0$.
\end{lemma}

>>>>

\title{
	On the characteristic and diameter of planar integral point sets
	\footnote{
		The work of the first author was partially supported by the Theoretical Physics
		and Mathematics Advancement Foundation “BASIS”.
	}
}

@@

\begin{lemma}
	\label{lem:pre_weeding_I}
	Any set $M = \{A, B, C\} \in \mathfrak{M}_3$ with edge $|AB| = m$, where $|AC| - |BC| = m - s$, $m, s \in \mathbb{N}$, $s$ is an odd number and $s \leq m$, has a characteristic of the form $p = 4k + 3$, $k \in \mathbb{N}_0$.
\end{lemma}
